### 2013-12-13 manuscripts/reply/short-reply.tex
Working on reply ms.
Moving Jake to acknowledgements.

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2}$, Jeet Sukumaran$^{3}$, Jacob A.\
        Esselstyn$^{4}$, Charles W.\ Linkem$^{5}$, Cameron D.\
        Siler$^{6}$, and Rafe M.\ Brown$^{1}$

        \bigskip
        $^1$\emph{Department of Ecology and Evolutionary Biology,
            Biodiversity Institute,
            University of Kansas,
            Lawrence, Kansas 66045}\\[.1in]
        $^3$\emph{Department of Biology,
            Duke University,
            Durham, North Carolina 27708} \\[.1in]
        $^4$\emph{Museum of Natural Science,
            Louisiana State University,
            119 Foster Hall,
            Baton Rouge, Louisiana 70803}\\[.1in]
        $^5$\emph{Department of Biology,
            University of Washington,
            Seattle, Washington 98195}\\[.1in]
        $^6$\emph{Sam Noble Museum,
            Department of Biology,
            University of Oklahoma,
            Norman, Oklahoma 73072}\\[.1in]
        $^2$\emph{Corresponding author} (\href{mailto:joaks1@gmail.com}{\tt
        joaks1@gmail.com})\\

@@

\section*{Acknowledgments}
J.\ Oaks thanks the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.

>>>>

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2}$, Jeet Sukumaran$^{3}$, Charles W.\ Linkem$^{4}$,
        Cameron D.\ Siler$^{5}$, and Rafe M.\ Brown$^{1}$

        \bigskip
        $^1$\emph{Department of Ecology and Evolutionary Biology,
            Biodiversity Institute,
            University of Kansas,
            Lawrence, Kansas 66045}\\[.1in]
        $^3$\emph{Department of Biology,
            Duke University,
            Durham, North Carolina 27708} \\[.1in]
        $^4$\emph{Department of Biology,
            University of Washington,
            Seattle, Washington 98195}\\[.1in]
        $^5$\emph{Sam Noble Museum,
            Department of Biology,
            University of Oklahoma,
            Norman, Oklahoma 73072}\\[.1in]
        $^2$\emph{Corresponding author} (\href{mailto:joaks1@gmail.com}{\tt
        joaks1@gmail.com})\\

@@

\section*{Acknowledgments}
We thank Jake Esselstyn for insightful comments that greatly improved this
work.
J.\ Oaks thanks the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
